---
title: "hiPSC models of Schizophrenia"
subtitle: 'Public release of data and code from Hoffman, et al. (submitted)'
author: "Developed by [Gabriel Hoffman](http://gabrielhoffman.github.io/)"
date: "Run on `r Sys.Date()`"
documentclass: article
output: 
  html_document:
  toc: true
---

Data is available on Synapse.

<!--- 
# run analysis
cd /media/sdb1/workspace/scripts/Brennand/COS/COS_public_release
rmarkdown::render("compare_differential_expression.Rmd")
--->


```{r initialize, cache=FALSE, echo=FALSE, message=FALSE, results='hide'}
nthreads = 12
```

```{r load.always, cache=FALSE, echo=FALSE, message=FALSE, results='hide'}
suppressPackageStartupMessages(library(synapseClient))

synapseLogin()

# dir.create("./results/differential_expression/Schizophrenia", recursive=TRUE)
# dir.create("./results/differential_expression/Cell_Composition/")
# dir.create("./results/differential_expression/Sendai/")
# dir.create("./results/variancePartition/")
```

```{r load.packages, echo=FALSE, message=FALSE, results='hide'}
library(ggplot2)
library(gridExtra)
library(grid)

options(xtable.type="html")

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=TRUE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  dev = c("png", "pdf"),   fig.width=7, fig.height=7)

options(markdown.HTML.stylesheet = 'css/custom.css')
```

# Compare differential expression results from current dataset to CommonMind and NIMH HBCC
```{r CMC.DE, cache=FALSE}

# CMC / DLPFC
# private: syn3493992
CMCDE = read.table(getFileLocation(synGet( 'syn5607603' )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
CMCDE$se = CMCDE$logFC / CMCDE$t

# HBCC / DLPFC microarray
CMCDE_HBCC = read.table(getFileLocation(synGet( 'syn4941553' )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
CMCDE_HBCC$se = CMCDE_HBCC$logFC / CMCDE_HBCC$t

# Read COS dataset
resDEall_Scz = read.table(getFileLocation(synGet( 'syn9920404' )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
rownames(resDEall_Scz) = resDEall_Scz$geneName
resDEall_Scz = resDEall_Scz[,-1]

# Read COS dataset: NPC
resDEall_Scz_NPC = read.table(getFileLocation(synGet( 'syn9920407' )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
rownames(resDEall_Scz_NPC) = resDEall_Scz_NPC$geneName
resDEall_Scz_NPC = resDEall_Scz_NPC[,-1]

# Read COS dataset: Neuron
resDEall_Scz_Neuron = read.table(getFileLocation(synGet( 'syn9920406' )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
rownames(resDEall_Scz_Neuron) = resDEall_Scz_Neuron$geneName
resDEall_Scz_Neuron = resDEall_Scz_Neuron[,-1]
```

```{r define.concordance.plots, fig.height=5.66, fig.width=17}
plot_concordance = function( df, square=TRUE ){

  if( square){
    lim = range(c(df$t.x, df$t.y))
    xlim = lim
    ylim = lim
  }else{
    xlim = range(df$t.x)
    ylim = range(df$t.y)
  }

  res = cor.test(df$t.x, df$t.y, method="pearson", alternative='greater')#, alternative="greater")
  txt = paste('R =', format(res$estimate, digits=3), '\np-value =', format(res$p.value, digits=2))
  res2 = cor.test(df$t.x, df$t.y, method="spearman", continuity=TRUE)#, alternative="greater")
  txt2 = paste('rho =', format(res2$estimate, digits=3), '\np-value =', format(res2$p.value, digits=2))
 
  ggplot(df, aes(t.x, t.y)) + geom_point() + theme_bw(15) + geom_abline(colour="grey", lty=2) + 
    geom_hline(yintercept = 0,colour="grey") +  xlim(xlim) +  ylim(ylim) + 
    geom_smooth(method = "lm", se = TRUE, color="firebrick")  + 
    annotate("text", x = min(xlim) * .9, y = max(ylim) * .9, label = paste(txt, txt2, sep="\n") , hjust=0) + 
    theme(plot.title = element_text(hjust = 0.5)) + theme(aspect.ratio=1)
}

plot_concordance_logFC = function( df, square=TRUE ){

  if( square){
    lim = range(c(df$logFC.x, df$logFC.y))
    xlim = lim
    ylim = lim
  }else{
    xlim = range(df$logFC.x)
    ylim = range(df$logFC.y)
  }

  res = cor.test(df$logFC.x, df$logFC.y, method="pearson", alternative='greater')#, alternative="greater")
  txt = paste('R =', format(res$estimate, digits=3), '\np-value =', format(res$p.value, digits=2))
  res2 = cor.test(df$logFC.x, df$logFC.y, method="spearman", continuity=TRUE, alternative="greater")
  txt2 = paste('rho =', format(res2$estimate, digits=3), '\np-value =', format(res2$p.value, digits=2))
 
  ggplot(df, aes(logFC.x, logFC.y)) + geom_point() + theme_bw(15) + geom_abline(colour="grey", lty=2) + 
    geom_hline(yintercept = 0,colour="grey") +  xlim(xlim) +  ylim(ylim) + 
    geom_smooth(method = "lm", se = TRUE, color="firebrick")  + 
    annotate("text", x = min(xlim) * .9, y = max(ylim) * .9, label = paste(txt, txt2, sep="\n") , hjust=0) + 
    theme(plot.title = element_text(hjust = 0.5)) + theme(aspect.ratio=1)
} 
```
## HBCC vs CommonMind
```{r HBCC_vs_CMC, fig.width=12, fig.height=8, message=FALSE}
df = merge(CMCDE, CMCDE_HBCC,by="genes")
fig1 = plot_concordance( df ) + ylab("t-statistic from HBCC") + xlab("t-statistic from CommonMind") + ggtitle("HBCC vs CommonMind")  
fig2 = plot_concordance_logFC( df ) + ylab("logFC from HBCC") + xlab("logFC from CommonMind") + ggtitle("HBCC vs CommonMind")    

grid.arrange( fig1, fig2, ncol=2)   
```

```{r}
addLabel = function(fig, txt){
  arrangeGrob(fig, top = textGrob(txt, x = unit(0, "npc")
         , y   = unit(1, "npc"), just=c("left","top"),
         gp=gpar(col="black", fontsize=18)))
}
```

## Combined COS dataset (neuron + NPC) compared to CMC and HBCC
```{r CMC_HBCC_COS, fig.height=12, fig.width=12, message=FALSE}
concordanceDF = matrix(NA, ncol=5, nrow=0)

# logFC
df = merge(CMCDE, resDEall_Scz,by.x="genes", by.y="row.names")  
corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "COS/combined", "logFC", corValues$estimate,  corValues$p.value))

fig1 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from COS/combined") + xlab("logFC from CommonMind") + ggtitle("CommonMind vs COS/combined (logFC)") 

df = merge(CMCDE_HBCC, resDEall_Scz,by.x="genes", by.y="row.names")
corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "COS/combined", "logFC", corValues$estimate,  corValues$p.value))

fig2 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from COS/combined") + xlab("logFC from HBCC") + ggtitle("HBCC vs COS/combined (logFC)") 

# t-statistics
df = merge(CMCDE, resDEall_Scz,by.x="genes", by.y="row.names")
corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "COS/combined", "t", corValues$estimate,  corValues$p.value))

fig3 = plot_concordance( df ) + ylab("t-statistic from COS/combined") + xlab("t-statistic from CommonMind") + ggtitle("CommonMind vs COS/combined (t-statistic)")

df = merge(CMCDE_HBCC, resDEall_Scz,by.x="genes", by.y="row.names")
corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "COS/combined", "t", corValues$estimate,  corValues$p.value))
fig4 = plot_concordance( df ) + ylab("t-statistic from COS/combined") + xlab("t-statistic from HBCC") + ggtitle("HBCC vs COS/combined (t-statistic)")

fig3 = addLabel(fig3, "A")
fig4 = addLabel(fig4, "B")
fig1 = addLabel(fig1, "C")
fig2 = addLabel(fig2, "D")

grid.arrange(fig3, fig4, fig1, fig2, ncol=2)   
```



# Differential expression in NPCs
```{r celltype.specific.NPC, fig.height=12, fig.width=12, message=FALSE}
df = merge(CMCDE, resDEall_Scz_NPC,by.x="genes", by.y="row.names")

corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "hiPSC-NPC", "t", corValues$estimate,  corValues$p.value))

corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "hiPSC-NPC", "logFC", corValues$estimate,  corValues$p.value))

fig1 = plot_concordance( df ) + ylab("t-statistic from hiPSC-NPC") + xlab("t-statistic from CommonMind") + ggtitle("hiPSC-NPC vs CommonMind")  
fig2 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from  hiPSC-NPC") + xlab("logFC from CommonMind") + ggtitle("hiPSC-NPC vs CommonMind")    

df = merge(CMCDE_HBCC, resDEall_Scz_NPC,by.x="genes", by.y="row.names")

corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "hiPSC-NPC", "t", corValues$estimate,  corValues$p.value))

corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "hiPSC-NPC", "logFC", corValues$estimate,  corValues$p.value))

fig3 = plot_concordance( df ) + ylab("t-statistic from hiPSC-NPC") + xlab("t-statistic from HBCC") + ggtitle("hiPSC-NPC vs HBCC")  
fig4 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from  hiPSC-NPC") + xlab("logFC from HBCC") + ggtitle("hiPSC-NPC vs HBCC")  

fig1 = addLabel(fig1, "A")
fig2 = addLabel(fig2, "B")
fig3 = addLabel(fig3, "C")
fig4 = addLabel(fig4, "D")

grid.arrange( fig1, fig3, fig2, fig4, ncol=2) 
```

# Differential expression in Neurons
```{r celltype.specific.Neuron, fig.height=12, fig.width=12, message=FALSE}
df = merge(CMCDE, resDEall_Scz_Neuron,by.x="genes", by.y="row.names")

corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "hiPSC-neuron", "t", corValues$estimate,  corValues$p.value))

corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("CommonMind", "hiPSC-neuron", "logFC", corValues$estimate,  corValues$p.value))


fig1 = plot_concordance( df ) + ylab("t-statistic from hiPSC-neuron") + xlab("t-statistic from CommonMind") + ggtitle("hiPSC-neuron vs CommonMind")  
fig2 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from  hiPSC-neuron") + xlab("logFC from CommonMind") + ggtitle("hiPSC-neuron vs CommonMind")    


df = merge(CMCDE_HBCC, resDEall_Scz_Neuron,by.x="genes", by.y="row.names")

corValues = with(df, cor.test(t.x, t.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "hiPSC-neuron", "t", corValues$estimate,  corValues$p.value))

corValues = with(df, cor.test(logFC.x, logFC.y, method="spearman"))
concordanceDF = rbind(concordanceDF, c("HBCC", "hiPSC-neuron", "logFC", corValues$estimate,  corValues$p.value))

fig3 = plot_concordance( df ) + ylab("t-statistic from hiPSC-neuron") + xlab("t-statistic from HBCC") + ggtitle("hiPSC-neuron vs HBCC")  
fig4 = plot_concordance_logFC( df, square=FALSE ) + ylab("logFC from  hiPSC-neuron") + xlab("logFC from HBCC") + ggtitle("hiPSC-neuron vs HBCC")    

fig1 = addLabel(fig1, "A")
fig2 = addLabel(fig2, "B")
fig3 = addLabel(fig3, "C")
fig4 = addLabel(fig4, "D")

grid.arrange( fig1, fig3, fig2, fig4, ncol=2) 
```


```{r concordance.barplot.logFC, fig.height=5}
concordanceDF = data.frame(concordanceDF, stringsAsFactors=FALSE)
colnames(concordanceDF) = c("dataset1", "dataset2", "stat", "rho", "pvalue")
concordanceDF$rho = as.numeric(concordanceDF$rho)
concordanceDF$pvalue = as.numeric(concordanceDF$pvalue)

collocal = c( "#FF8D1E", "#1E90FF")

# statistic = "logFC"

# fig1 = ggplot(subset(concordanceDF, stat==statistic & dataset2=="COS"), aes(dataset1, rho, fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
#   guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(15) +
#   theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/4) +
#   coord_flip() + scale_fill_manual(values=collocal) + theme(axis.text.y= element_blank())

# fig2 = ggplot(subset(concordanceDF, stat==statistic & dataset2=="COS"), aes(dataset1, -log10(pvalue), fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(-log[10]~p-value)) +
#   guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(15) +
#   theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/4) +
#   coord_flip() + scale_fill_manual(values=collocal) + theme(axis.text.y= element_blank())

# grid.arrange(fig1, fig2, ncol=1)
```

```{r concordance.barplots.t, fig.height=5}
# statistic = "t"

# fig3 = ggplot(subset(concordanceDF, stat==statistic & dataset2=="COS"), aes(dataset1, rho, fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
#   guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(15) +
#   theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/4) +
#   coord_flip() + scale_fill_manual(values=collocal) + theme(axis.text.y= element_blank())

# fig4= ggplot(subset(concordanceDF, stat==statistic & dataset2=="COS"), aes(dataset1, -log10(pvalue), fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(-log[10]~p-value)) +
#   guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(15) +
#   theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/4) +
#   coord_flip() + scale_fill_manual(values=collocal) + theme(axis.text.y= element_blank())

# grid.arrange(fig3, fig4, ncol=1)
```


## Concordance between COS and CommonMind/HBCC based on logFC 
```{r combined.logFC}

statistic = "logFC"

fig1 = ggplot(subset(concordanceDF, stat==statistic), aes(dataset2, rho, fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/2) +
  coord_flip() + scale_fill_manual(values=collocal) 

fig2 = ggplot(subset(concordanceDF, stat==statistic), aes(dataset2, -log10(pvalue), fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') +  ylab(bquote(-log[10]~p-value)) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/2) +
  coord_flip() + scale_fill_manual(values=collocal) 

grid.arrange(fig1, fig2, ncol=1)
```


## Concordance between COS and CommonMind/HBCC based on t-statistics
```{r combined.t}
statistic = "t"

fig1 = ggplot(subset(concordanceDF, stat==statistic), aes(dataset2, rho, fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/2) +
  coord_flip() + scale_fill_manual(values=collocal) 

fig2 = ggplot(subset(concordanceDF, stat==statistic), aes(dataset2, -log10(pvalue), fill=dataset1)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') +  ylab(bquote(-log[10]~p-value)) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), aspect.ratio=1/2) +
  coord_flip() + scale_fill_manual(values=collocal) 

grid.arrange(fig1, fig2, ncol=1)
```


# Concordance between COS and CommonMind/HBCC based on t-statistics, when including different cell type composition scores as covariates
```{r DE.all.CTC.scores}
cibersort = read.table(getFileLocation(synGet( 'syn9908124' )), row.names=1, header=TRUE)
rownames(cibersort) = gsub("-2$", "R", rownames(cibersort))

filesDF = synQuery('select * from file where parentId == "syn9920830"')

concordanceDFall = matrix(NA, ncol=6, nrow=0)

for(covariate in c('NULL',colnames(cibersort)) ){

  file = paste0('COS_DE_SZNeuron_', covariate, ".tsv")
  id = filesDF$file.id[match(file,filesDF$file.name)]
  resDEall_Scz_Neuron = read.table(getFileLocation(synGet( id )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
  rownames(resDEall_Scz_Neuron) = resDEall_Scz_Neuron$geneName
  resDEall_Scz_Neuron = resDEall_Scz_Neuron[,-1]


  file = paste0('COS_DE_SZNPC_', covariate, ".tsv")
  id = filesDF$file.id[match(file,filesDF$file.name)]
  resDEall_Scz_NPC = read.table(getFileLocation(synGet( id )), header=TRUE, stringsAsFactors=FALSE, sep='\t')
  rownames(resDEall_Scz_NPC) = resDEall_Scz_NPC$geneName
  resDEall_Scz_NPC = resDEall_Scz_NPC[,-1]

  # NPC
  df = merge(CMCDE, resDEall_Scz_NPC,by.x="genes", by.y="row.names")
  corValues = with(df, cor.test(t.x, t.y, method="spearman"))
  concordanceDFall = rbind(concordanceDFall, c("CommonMind", "hiPSC-NPC", covariate, "t", corValues$estimate,  corValues$p.value))
  fig1 = plot_concordance( df ) + ylab("t-statistic from hiPSC-NPC") + xlab("t-statistic from CommonMind") + ggtitle("hiPSC-NPC vs CommonMind")  

  df = merge(CMCDE_HBCC, resDEall_Scz_NPC,by.x="genes", by.y="row.names")
  corValues = with(df, cor.test(t.x, t.y, method="spearman"))
  concordanceDFall = rbind(concordanceDFall, c("HBCC", "hiPSC-NPC", covariate, "t", corValues$estimate,  corValues$p.value))
  fig2 = plot_concordance( df ) + ylab("t-statistic from hiPSC-NPC") + xlab("t-statistic from HBCC") + ggtitle("hiPSC-NPC vs HBCC")  

  # Neuron
  df = merge(CMCDE, resDEall_Scz_Neuron,by.x="genes", by.y="row.names")
  corValues = with(df, cor.test(t.x, t.y, method="spearman"))
  concordanceDFall = rbind(concordanceDFall, c("CommonMind", "hiPSC-neuron", covariate, "t", corValues$estimate,  corValues$p.value))
  fig3 = plot_concordance( df ) + ylab("t-statistic from hiPSC-neuron") + xlab("t-statistic from CommonMind") + ggtitle("hiPSC-neuron vs CommonMind")  

  df = merge(CMCDE_HBCC, resDEall_Scz_Neuron,by.x="genes", by.y="row.names")
  corValues = with(df, cor.test(t.x, t.y, method="spearman"))
  concordanceDFall = rbind(concordanceDFall, c("HBCC", "hiPSC-neuron", covariate, "t", corValues$estimate,  corValues$p.value))
  fig4 = plot_concordance( df ) + ylab("t-statistic from hiPSC-neuron") + xlab("t-statistic from HBCC") + ggtitle("hiPSC-neuron vs HBCC")  

  # grid.arrange( fig1, fig3, fig2, fig4, ncol=2) 
}
```

```{r plot.concordance.rho, fig.width=16,fig.height=16}
concordanceDFall = data.frame(concordanceDFall, stringsAsFactors=FALSE)
colnames(concordanceDFall) = c("dataset1", "dataset2", "covariate", "stat", "rho", "pvalue")
concordanceDFall$rho = as.numeric(concordanceDFall$rho)
concordanceDFall$pvalue = as.numeric(concordanceDFall$pvalue)

# rename fibroblast
concordanceDFall$covariate[with(concordanceDFall, covariate=='Fibroblast')] = 'Fibroblast1'
concordanceDFall$covariate[with(concordanceDFall, covariate=='MEF')] = 'Fibroblast2'

collocal = c( "orange", "green2")

statistic = "t"   

fig1 = ggplot(subset(concordanceDFall, stat==statistic & dataset1=='CommonMind'), aes(covariate, rho, fill=dataset2)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), legend.position="top", aspect.ratio=2) +
  coord_flip() + scale_fill_manual(values=collocal) + ggtitle("Concordance with CommonMind")

fig2 = ggplot(subset(concordanceDFall, stat==statistic & dataset1=='HBCC'), aes(covariate, rho, fill=dataset2)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(Correlation~(Spearman~rho))) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), legend.position="top", aspect.ratio=2) +
  coord_flip() + scale_fill_manual(values=collocal) + ggtitle("Concordance with HBCC")

statistic = "t"   

fig3 = ggplot(subset(concordanceDFall, stat==statistic & dataset1=='CommonMind'), aes(covariate, -log10(pvalue), fill=dataset2)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('')  + ylab(bquote(-log[10]~p-value)) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), legend.position="none", aspect.ratio=2) +
  coord_flip() + scale_fill_manual(values=collocal) + ggtitle("Concordance with CommonMind")

fig4 = ggplot(subset(concordanceDFall, stat==statistic & dataset1=='HBCC'), aes(covariate,  -log10(pvalue), fill=dataset2)) + geom_bar(stat='identity', position=position_dodge()) +  xlab('') + ylab(bquote(-log[10]~p-value)) +
  guides(fill=guide_legend(title="Post mortem datasets")) + theme_bw(16) +
  theme(plot.title=element_text(hjust=0.5), legend.position="none", aspect.ratio=2) +
  coord_flip() + scale_fill_manual(values=collocal) + ggtitle("Concordance with HBCC")


fig1 = addLabel(fig1, "A")
fig2 = addLabel(fig2, "B")
fig3 = addLabel(fig3, "C")
fig4 = addLabel(fig4, "D")

 grid.arrange( fig1, fig2, fig3, fig4, ncol=2) 
```
